\documentclass[12pt]{report}
\setcounter{secnumdepth}{1}
\setcounter{tocdepth}{5}

\usepackage{amsmath,amssymb,epsfig,graphicx,multirow}
\usepackage{setspace}
\usepackage{outlines}
\DeclareGraphicsRule{.JPG}{eps}{*}{`jpeg2ps #1}

\setlength{\topmargin}{-1in}
\setlength{\oddsidemargin}{-.0in}
\setlength{\evensidemargin}{-.2in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10.0in}

\begin{document}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[subsection]{Definition}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{notation}[1][Notation]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{problem}[1][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{homework}[1][Homework]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
    

\newcommand{\ds}{\displaystyle}

\renewcommand*\thesection{\arabic{section}}
\doublespacing
\begin{center}
	\large Senior Thesis Outline
\end{center}
\singlespacing
\begin{outline}[enumerate]
\1 Introduction
	\2 Historical Background
	\2 Motivation
		\3 Image Analysis
		\3 Dynamical Systems?
		\3 Ghrist's Examples?
\1 Simplicial Homology
	\2 Complexes and Chains
	\2 Boundary Operator
	\2 Computing Homology (By Hand)
\1 Cubical Homology
	\2 Why Cubical Homology?
	\2 $k$-cubes and $k$-chains
	\2 Boundary Operator
	\2 Computing Homology (By Hand)
\1 Computational Homology
	\2 Smith-Normal Form
	\2 Computing Homology of Cubical Sets
	\2 Algorithms?
	\2 Optimization?
	\2 Reduction
\1 CHomP?
	\2 Discussion of basic operation?
	\2 Examples of Input $\Rightarrow$ Output?
\1 Interesting Examples?
	\2 Fingerprints?
	\2 Counting Stars?
	\2 Path Finding $\Rightarrow$ Maze Solving?
	\2 Minecraft???
\1 Conclusion
\end{outline}
\end{document}